A tutorial on the model-dependent analysis of neutron and X-ray reflectometry

### 2020-07-08 refl_maths/paper.tex
fix
start con var

When we measure a reflectometry profile, we measure the reflected intensity, and some uncertainty in that measurement, at discrete points in the wavevector, $R(q) \pm \delta R(q)$. 
Using the recursive method discussed above, we can calculate a model reflected intensity at these same $q$ values, $R_m(q)$. 
We then aim to reduce the difference between the measured and modelled reflected intensity through the optimisation (maximisation) of the likelihood, $L$, 
%
\begin{equation}
    \begin{aligned}
        L & = \exp{\bigg\{- \frac{1}{2} \sum_{q=q_{\text{min}}}^{q_{\text{max}}} \bigg[\frac{R(q) - R_m(q)}{\delta R(q)}\bigg]^2 \\
        & + \ln[2\pi \delta R(q)]\bigg\}}.
    \end{aligned}
\end{equation}
%
This parameter described the probability that the model $m$ accurately describes the observed reflectometry data. 
The aim in reflectometry modelling is to obtain a model reflectometry that has the maximum likelihood possible for the given experimental data. 
Figure~\ref{fig:likelihood} shows the maximum likelihood model for some experimental data, in addition to another model which does not agree well with the data and therefore has a lower likelihood as a result. 
%
\begin{figure}[t]
    \includegraphics[width=0.49\textwidth]{likelihood}
    \caption{The maximum likelihood fit, the blue data points indicate some experimental data, while the yellow line shows the maximum likelihood model fit to this dataset and the green line show another model (which doesn't maximise the likelihood).}
    \label{fig:likelihood}
\end{figure}
%

@@

>>>>

When we measure a reflectometry profile, we measure the reflected intensity, and some uncertainty in that measurement, at discrete points in the wavevector, $R(q) \pm \delta R(q)$. 
Using the recursive method discussed above, we can calculate a model reflected intensity at these same $q$ values, $R_m(q)$. 
We then aim to reduce the difference between the measured and modelled reflected intensity through the optimisation (maximisation) of the likelihood, $L$, 
%
\begin{equation}
    \begin{aligned}
        L = \exp\bigg\{ & - \frac{1}{2} \sum_{q=q_{\text{min}}}^{q_{\text{max}}} \bigg[\frac{R(q) - R_m(q)}{\delta R(q)}\bigg]^2 \\
         & + \ln[2\pi \delta R(q)]\bigg\}.
    \end{aligned}
\end{equation}
%
This parameter described the probability that the model $m$ accurately describes the observed reflectometry data. 
The aim in reflectometry modelling is to obtain a model reflectometry that has the maximum likelihood possible for the given experimental data. 
Figure~\ref{fig:likelihood} shows the maximum likelihood model for some experimental data, in addition to another model which does not agree well with the data and therefore has a lower likelihood as a result. 
%
\begin{figure}[t]
    \includegraphics[width=0.49\textwidth]{likelihood}
    \caption{The maximum likelihood fit, the blue data points indicate some experimental data, while the yellow line shows the maximum likelihood model fit to this dataset and the green line show another model (which doesn't maximise the likelihood).}
    \label{fig:likelihood}
\end{figure}
%

@@

\section{Contrast variation/resonant reflectometry}
Contrast variation is an important tools in neutron reflectometry \cite{bohm_probing_2019,clifton_self_2019}, while the use of resonant X-ray reflectometry may be utilised in the study of magnetic or ferroelectric materials \cite{kemik_resonant_2011}. 
These techniques differ significantly in the practical experimental methodology, however there is substantial overlap in their analysis. 
In theory, both methods enable the ability to measure identical structural samples with variations in the scattering lengths of the components.
